---
title: "Price Patterns and Stock Status: Analyzing 'Club House' Brand Strategies"
author: Yizhuo Li
format: pdf
date: November 14, 2024
date-format: long
abstract: This paper explores "Club House" product pricing and stock status impact, using data from the Filipp Hammer database. Results show most products priced low, with slight price differences by stock status. Caution is advised due to causation, missing data, and bias concerns, providing insights into potential influences on Club House’s pricing strategy.
bibliography: references.bib
---

# Introduction
This analysis focuses on examining the price distribution of products and the potential impact of stock status on pricing for the brand "Club House." The data used in this study is derived from Filipp’s Hammer database [@Filipp_Hammer] and analyzed using the programming language R [@citeR]. By exploring detailed information on Club House products—including product names, prices, and stock levels—this analysis aims to uncover insights into the brand's pricing strategies and possible trends in consumer demand.

# Measurement
In Project Hammer, the process of transforming real-world grocery price fluctuations into SQL database entries involves several key steps. Data is first collected through automated scripts that scrape prices from major grocery retailers’ websites. This raw data is then cleansed and standardized to ensure accuracy and consistency across different sources. The cleaned data is structured into an SQL database, which facilitates complex queries and analyses. Metadata documentation accompanies the dataset, detailing collection methods, measurement units, and frequency, which supports transparency and data integrity.

# Result
```{r}
#| label: fig-figure1
#| echo: false
#| warning: false
library(ggplot2)
library(dplyr)

# 读取数据
data <- read.csv("a.csv")

# 清理数据：移除current_price中为空的值，并确保数据为数值型
data_cleaned <- data %>%
  filter(!is.na(current_price)) %>%
  mutate(current_price = as.numeric(current_price))

# 绘制价格分布的密度图，并将 x 轴限制在 0 到 20
ggplot(data_cleaned, aes(x = current_price)) +
  geom_density(fill = "skyblue", alpha = 0.5) +
  labs(title = "Price Distribution of All Products",
       x = "Current Price",
       y = "Density") +
  xlim(0, 20) +
  theme_minimal()

# 如果更喜欢直方图，可以用以下代码替换密度图代码：
# ggplot(data_cleaned, aes(x = current_price)) +
#   geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +
#   labs(title = "Price Distribution of All Products",
#        x = "Current Price",
#        y = "Frequency") +
#   xlim(0, 20) +
#   theme_minimal()

```
@fig-figure1 illustrates the price distribution for all products. The distribution is notably multi-modal, with several prominent peaks within the 0 to 10 price range, indicating clusters of product prices around specific values. The density drops sharply beyond a price of 10, with very few products priced above this threshold. This skewed distribution suggests that most products fall within a lower price bracket, with some variation around certain price points. The data could indicate different tiers or categories of products grouped around particular price levels, though it is unclear if external factors (such as promotions or seasonal pricing) might influence these clusters.
```{r}
#| label: fig-figure2
#| echo: false
#| warning: false
# 加载必要的库
library(ggplot2)
library(dplyr)

# 假设数据已加载为 data 数据框
# 将 'other' 列分成三类：'Low Stock'，'Out of Stock' 和 'Available'
data_cleaned <- data %>%
  mutate(stock_status = case_when(
    grepl("Low", other, ignore.case = TRUE) ~ "Low Stock",
    grepl("Out", other, ignore.case = TRUE) ~ "Out of Stock",
    TRUE ~ "Available"
  ))

# 移除current_price中为空的值
data_cleaned <- data_cleaned %>% filter(!is.na(current_price))

# 绘制箱线图
ggplot(data_cleaned, aes(x = stock_status, y = as.numeric(current_price))) +
  geom_boxplot() +
  labs(title = "Product Price Distribution by Stock Status",
       x = "Stock Status",
       y = "Current Price") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
\newpage
@fig-figure2 presents a comparison of product prices across different stock statuses (Available, Low Stock, Out of Stock) using box plots. Products marked as “Available” have a wide range of prices, with a moderate median price and several high outliers. "Low Stock" products appear to have a slightly higher median price, but the range is more condensed, with fewer extreme values. “Out of Stock” products also show a wide range, although their median is similar to the “Available” category. This breakdown suggests potential pricing differences associated with inventory status, though additional analysis is needed to determine if there is any causal relationship between stock status and price.

# Discussion
## Correlation vs. Causation

In analyzing the relationship between stock status and pricing, it's important to differentiate correlation from causation. The observed data may show a pattern where higher-priced products frequently have lower stock levels, potentially leading to the assumption that scarcity directly drives up prices. However, this correlation does not confirm causation. It could also be that higher-priced items are stocked less due to lower turnover rates or strategic business decisions regarding inventory management. Establishing a true causal link would require a deeper analysis into the decision-making processes of suppliers and retailers regarding stock levels and pricing adjustments.

## Missing Data

The integrity of conclusions drawn from data analysis is significantly impacted by the completeness of the dataset. Missing data, particularly if systematic (e.g., consistently missing data for certain price ranges or during specific periods), can skew the analysis. For example, if higher-priced items are underreported, this might falsely suggest a prevalence of lower prices across the board. The absence of comprehensive data hampers the ability to accurately depict the true nature of pricing and stock dynamics, potentially leading to erroneous strategic recommendations.

## Sources of Bias

Bias in data collection and analysis can critically alter the outcomes and interpretations of research. In the context of Project Hammer, potential biases might arise from several sources, including the overrepresentation of data from particular vendors, time periods, or promotional sales. These biases could inadvertently favor certain price ranges or stock statuses, misleading conclusions about general market conditions. To mitigate these effects, it's necessary to employ rigorous sampling methods, ensure a balanced representation of all relevant categories, and critically evaluate the influence of promotional activities on price and stock data.
# Reference
